---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RSOQuestions

RSOQuestions is a way to easily view / run the code of questions on the `r` tag on stackoverflow.

## Installation

You can install RSOQuestions from GitHub with:

``` r
devtools::install_github("d-edison/RSOQuestions")
```

## Example

You can grab a question from stackoverflow by using the `get_question` function and providing a question ID (found in the URL of the question):

```{r}
library(RSOQuestions)

# this ID corresponds to a popular question on the differences between <- and = for assignment
q <- get_question(id = 1741820) 
```

If no arguments are provided to `get_question`, the most recent question on the `r` tag will be used by default. RSOQuestions also provides a convenience function `get_recent_ids` to grab the 30 most recent IDs on the `r` tag:

```{r}
get_recent_ids()
```

To view the question in the RStudio Viewer pane, use `view_question`:

```{r, eval = FALSE}
view_question(q)
```

You run anything formatted as code with `run_code`. This function will run all expressions in the global environment and capture all results and errors:

```{r}
# run all code in global environment
res <- run_code(q) 

# see results
res
```
 
